02_DESeq2

### 2020-05-09 analysis/02_DESeq2.Rmd
better fig 1
fig 4 updates

>>>>

str(HP)
```

## FOR DEGs of all TREATMENT comparsions, char y manip

```{r}
countData <- read.csv("../results/00_counts.csv", header = T, row.names = 1)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)
colData <- read.csv("../metadata/00_samples.csv", header = T, row.names = 1)

colData$sextissue <- as.factor(paste(colData$sex, colData$tissue, sep = "_"))
colData$treatment <- factor(colData$treatment, levels = alllevels)
colData$tissue <- factor(colData$tissue, levels = tissuelevel)
levels(colData$treatment)
levels(colData$sex)
levels(colData$sextissue)
levels(colData$tissue)
colData <- colData %>% drop_na()
# 987 samples, 8 variables

createDEGdftreatment <- function(up, down, mytissue){

  partialfilename = paste("_", down, "_", up, sep = "")
  myfilename = paste0("../results/DESeq2/treatment/", mytissue, partialfilename, "_DEGs.csv")

  myfilename = paste0("../results/DEseq2/treatment/", i, "_vsd.csv")
  write.csv(vsd, myfilename)

  # save differential gene expression results

  control.bldg <- createDEGdftreatment("bldg", "control", i)
  bldg.lay <- createDEGdftreatment("lay", "bldg", i)
  lay.inc.d3 <- createDEGdftreatment("inc.d3", "lay",  i) 
  inc.d3.inc.d9 <- createDEGdftreatment("inc.d9", "inc.d3", i) 
  inc.d9.inc.d17 <- createDEGdftreatment("inc.d17", "inc.d9", i)
  inc.d17.hatch <- createDEGdftreatment( "hatch", "inc.d17", i) 
  hatch.n5 <- createDEGdftreatment( "n5", "hatch",  i) 
  n5.n9 <- createDEGdftreatment("n9", "n5",  i)

  control.lay <- createDEGdftreatment("lay", "control", i)
  control.inc.d3 <- createDEGdftreatment("inc.d3", "control",  i) 
  control.inc.d9 <- createDEGdftreatment("inc.d9", "control", i) 
  control.inc.d17 <- createDEGdftreatment("inc.d17", "control", i)
  control.hatch <- createDEGdftreatment( "hatch", "control", i) 
  control.n5 <- createDEGdftreatment( "n5", "control",  i) 
  control.n9 <- createDEGdftreatment("n9", "control",  i)

  control.extend <- createDEGdftreatment("extend", "control",  i) 
  control.prolong <- createDEGdftreatment("prolong", "control",  i) 
  control.early <- createDEGdftreatment("m.inc.d8", "control",  i)

  control.m.inc.d3 <- createDEGdftreatment("m.inc.d3", "control",  i) 
  control.m.inc.d9 <- createDEGdftreatment("m.inc.d9", "control",  i) 
  control.m.inc.d17 <- createDEGdftreatment("m.inc.d17", "control",  i)
  control.m.n2 <- createDEGdftreatment("m.n2", "control",  i)

  bldg.inc.d3 <- createDEGdftreatment("inc.d3", "bldg",  i) 
  bldg.inc.d9 <- createDEGdftreatment("inc.d9", "bldg", i) 
  bldg.inc.d17 <- createDEGdftreatment("inc.d17", "bldg", i)
  bldg.hatch <- createDEGdftreatment( "hatch", "bldg", i) 
  bldg.n5 <- createDEGdftreatment( "n5", "bldg",  i) 
  bldg.n9 <- createDEGdftreatment("n9", "bldg",  i)

  bldg.extend <- createDEGdftreatment("extend", "bldg",  i) 
  bldg.prolong <- createDEGdftreatment("prolong", "bldg",  i) 
  bldg.early <- createDEGdftreatment("m.inc.d8", "bldg",  i)

  bldg.m.inc.d3 <- createDEGdftreatment("m.inc.d3", "bldg",  i) 
  bldg.m.inc.d9 <- createDEGdftreatment("m.inc.d9", "bldg",  i) 
  bldg.m.inc.d17 <- createDEGdftreatment("m.inc.d17", "bldg",  i)
  bldg.m.n2 <- createDEGdftreatment("m.n2", "bldg",  i)

  hatch.m.n2 <- createDEGdftreatment("m.n2", "hatch",  i) 
  hatch.prolong <- createDEGdftreatment("prolong", "hatch",  i) 
  hatch.m.inc.d8 <- createDEGdftreatment("prolong", "hatch",  i)

  inc.d17.m.n2 <- createDEGdftreatment("m.n2", "inc.d17",  i) 
  inc.d17.prolong <- createDEGdftreatment("prolong", "inc.d17",  i)

  prolong.extend <- createDEGdftreatment("extend", "prolong",  i) 
  early.extend <- createDEGdftreatment("extend", "m.inc.d8",  i) 
  early.prolong <- createDEGdftreatment("prolong", "m.inc.d8",  i)

  m.inc.d9.m.inc.d3 <- createDEGdftreatment("m.inc.d9", "m.inc.d3",  i) 
  m.inc.d17.m.inc.d9 <- createDEGdftreatment("m.inc.d17", "m.inc.d9",  i) 
  m.inc.d17.m.inc.d3 <- createDEGdftreatment("m.inc.d17", "m.inc.d3",  i) 
  m.n2.m.inc.d17 <- createDEGdftreatment("m.n2", "m.inc.d17",  i) 
  m.n2.m.inc.d9 <- createDEGdftreatment("m.n2", "m.inc.d9",  i)
  m.n2.m.inc.d3 <- createDEGdftreatment("m.n2", "m.inc.d3",  i)

  m.inc.d3.inc.d3 <- createDEGdftreatment("m.inc.d3", "inc.d3",  i) 
  m.inc.d9.inc.d9 <- createDEGdftreatment("m.inc.d9", "inc.d9",  i) 
  m.inc.d17.inc.d17 <- createDEGdftreatment("m.inc.d17", "inc.d17",  i) 
  m.n2.hatch <- createDEGdftreatment("m.n2", "hatch",  i)

}
